Verifying Demonstrations

### 2019-02-13 paper/distance-bounding.tex
adds references to appendices
Minor edits about DB protocols in general

The main attacks against \ac{DB} protocols can be summarized as follows:
\begin{itemize}
  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using an honest prover far away from the verifier.
  \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but uses an unsuspecting honest prover close to the verifier to pass as being close.
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against a verifier who will attempt to impersonate the prover.
More specifically, we must combine such \iac{PPK} protocol with anonymous 
credentials.
The choice of the anonymous-credential system affects the properties we 
require of the \ac{PPK}, in particular, for the suggested instantiation it must 
be \iac{PPK} for discrete logarithms.
For this paper, we assume the existence of such a protocol. Candidates for such a protocol include modifications of ~\cite{ProProx} or ~\cite{PROPS} to work for discrete logarithm and to provide general attribute-based anonymous credentials (not restricted to identity-based ones), respectively.

>>>>

There are four adversaries for \ac{DB} protocols established in the literature, 
each of which tries to commit a type of fraud.
These can be summarized as follows:
\begin{itemize}
  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \Acf{DBMF}: the adversary illegitimately authenticates using a, 
    possibly honest, prover who is far away from the verifier.
    (Also known as relaying attack or man-in-the-middle attack.)
  \item \Acf{DBTF}: a legitimate, but malicious, prover helps an accomplice, 
    who is close to the verifier, to authenticate.
    \Ac{DBTF} resistance is a very strong property; it implies that if the 
    accomplice succeeds (with non-negligible probability) he will learn the 
    prover's secret key.
  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but 
    uses an unsuspecting honest prover close to the verifier to pass as being 
    close.
    (This is different from \ac{DBMF} in that the honest prover actually tries 
    to authenticate to the verifier, but the malicious prover hijacks the 
    channel at some point(s) during the protocol.)
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to 
their actions, thus we also require strong privacy.
In fact, as the construction in \cref{CROCUS} shows, we require \iac{DB} 
\ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.
